---
title: "P8105 Homework 6"
author: "Diana Hernandez"
date: "2023-12-02"
output: github_document
---

Load libraries and settings.

```{r}
library(tidyverse)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal())

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

Import dataset.

```{r}
homicide_data =
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
```

Create `city_state` variable and binary variable indicating whether the homicide is solved.

```{r}
homicide_tidy = 
  homicide_data |>
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    ),
    victim_age = as.numeric(victim_age)
  ) |>
  filter(
    !city_state %in% c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO"),
    victim_race %in% c("White", "Black")) 
```

For the city of Baltimore, MD, use the `glm` function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors.

```{r}
baltimore_df =
  homicide_tidy |>
  filter(city_state == "Baltimore, MD") |>
  mutate(
    resolution = as.numeric(resolution == "unsolved")
  )

baltimore_fit_logistic =
  baltimore_df |>
  glm(resolution ~ victim_age + victim_race + victim_sex, data = _, family = binomial()) 
```

Estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
baltimore_fit_logistic |> 
  broom::tidy() |> 
  mutate(OR = exp(estimate)) |>
  select(term, log_OR = estimate, OR, p.value) |> 
  knitr::kable(digits = 3)
```

Run `glm` for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims.

# Problem 2

Import dataset.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Bootstrapping SLR with `tmax` as the response with `tmin` and `prcp` as the predictors.

```{r}
weather_df |> 
  modelr::bootstrap(n = 5000) |> 
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = df)),
    results = map(models, broom::tidy),
    rsquared = map(models, broom::glance))|> 
  select(results, rsquared) |> 
  unnest(rsquared) |>
  select(results, r.squared) |>
  unnest(results) |>
  select(term, estimate, r.squared) |>
  mutate(term = as.factor(term)) |>
  pivot_wider(
    names_from = "term", 
    values_from = "estimate",
    names_prefix = "beta_") |>
  mutate(
    log_beta1beta2 = log(beta_tmin*beta_prcp)
  )
```

# Problem 3

Import dataset.

```{r}
birthweight = read_csv("./data/birthweight.csv")
```

